\documentclass{bioinfo}
\copyrightyear{2015}
\pubyear{2015}

\usepackage{hyperref}

\begin{document}
\firstpage{1}

\title[short Title]{NodeJS}
\author[Sample \textit{et~al}]{Corresponding Author: Arved Baus, Mohd Ahmed Khan	}

\address{Department of XXXXXXX, Address XXXX }

\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

\editor{Associate Editor: XXXXXXX}

\maketitle

\begin{abstract}

\section{Motivation:}
\href{www.nodejs.org}{Node.js} is a platform to build fast, scalable network applications. To reach this goal it runs in Chrome's JavaScript runtime Engine V8. Furthermore it uses an event driven and non-blockig IO model to ensure lightweight and efficiency. Many companies such as Uber, ebay and PayPal successfully integrated NodeJS in their development stack. To analyse the advantages of using NodeJS a project will be developed with it. 

\section{Results:}
The resulting project is a website where you can bet on football against your friends. It shows main concepts of NodeJS such as non-blocking Input/Output and its event driven model. To present the results in the final presentation a fake server has to be deployed which delivers random events during  a football match. 

\section{Availability:} NodeJs is licensed under the MIT-licence which allows its use for commercial and non-commercial projects. It is under active development and open source. The files are available on Github.

\section{Contact:} \href{arved.baus@tum.de}{arved.baus@tum.de} \&  \href{mahmedk91@gmail.com}{mahmedk91@gmail.com}
\end{abstract}

\section{Why Node.js}
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. 
\section{MiniWeb - App}
\subsection{Architecture in detail}
\subsection{Used technologies}

\section{Single Threaded}
\subsection{Scalability}
\subsection{CPU intensive operations}

\section{Import Modules}
\subsection{Socket.IO}
\subsection{expressJS}
\subsection{?}

\section{Multi-threading}
\subsection{Traditional Threaded Web Applications}
\subsection{NodeJS approach}

\section{Discussion}
\subsection{Advantages of using NodeJS}
\subsection{Disadvantages of using NodeJS}

\subsection{Conclusion}

(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Figure \ref{fig:02} shows that the above method  Text Text Text Text  Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Figure \ref{fig:02} shows that the above method  Text Text Text Text  Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Figure \ref{fig:02} shows that the above method  Text Text Text Text  Text Text Text Text Text Text  Text Text.



Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Figure \ref{fig:02} shows that the above method  Text Text Text Text  Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text text text text





\begin{enumerate}
\item this is item, use enumerate
\item this is item, use enumerate
\item this is item, use enumerate
\end{enumerate}

Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Figure \ref{fig:02} shows that the above method  Text Text Text Text  Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Figure \ref{fig:02} shows that the above method  Text Text Text Text  Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.






Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Figure \ref{fig:02} shows that the above method  Text Text Text Text


\section*{Acknowledgement}
Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text text text text

\paragraph{Funding\textcolon} Text Text Text Text Text Text  Text Text.

%\bibliographystyle{natbib}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{bioinformatics}
%
%\bibliographystyle{plain}
%
%\bibliography{Document}


\begin{thebibliography}{}
\bibitem[Dayley {\it et~al}.,2014 F]{Dayley01} Dayley, B. (2015) Node.js, MongoDB and AnularJS Web Development.

\end{thebibliography}
\end{document}
